% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Michael Barnes, P.E.}

\basicInfo{
  \email{michael.sergio.barnes@gmail.com} \textperiodcentered\ 
  \phone{(626) 833-3995} \textperiodcentered\ 
  \faHome \ \href{https://maikeulb.github.io}{maikeulb.github.io} \textperiodcentered
  \github[maikeulb]{https://github.com/maikeulb} 
  }

\section{\faCode\ Projects}
\datedsubsection{\textbf{Filmogram} | \textit{Python, Flask, PostgreSQL, JavaScript, UI Kit, Docker, Nginx}}{ }
Social network for film photographers: users share their favorite photos with other users.
\begin{itemize}
  \item Implemented activity feed, user profile, photo upload, user discovery, 
          photo favorite, user follow/unfollow, and
          admin features. Deployed onto DigitalOcean VM and tested with Pytest.
   \item \textit{Live: \href{https://filmogram.net}{filmogram.net} | 
                 Source: \href{https://github.com/maikeulb/filmogram}{github.com/maikeulb/filmogram}}

\end{itemize}

%\datedsubsection{\textbf{PhotoExhibiter} | \textit{C\#, ASP.NET Core, MySQL, JavaScript, Bootstrap 4, Docker, Nginx}}{}
%Social network for photo enthusiasts: users showcase their photography exhibits
%and attend other users' exhibits.
%\begin{itemize}
%  \item Implemented activity feed, user profile, exhibit post, exhibit attendance, user follow/unfollow, and admin
%          features. Deployed onto DigitalOcean VM and tested with xUnit.
%  \item \textit{Live: \href{http://167.99.53.202}{http://167.99.53.202} | 
%                Source: \href{https://github.com/maikeulb/photoexhibiter}{github.com/maikeulb/photoexhibiter}}
%\end{itemize}

\datedsubsection{\textbf{RolleiShop} | \textit{C\#, ASP.NET Core, PostgreSQL, Redis, JavaScript, Semantic UI, Docker, Nginx}}{}
E-commerce application for medium format cameras.
\begin{itemize}
  \item Implemented catalog (cached with Redis), shopping cart, order processing (Stripe integration), order history, email confirmation, localization (translated to Japanese), and admin features. Deployed onto DigitalOcean VM and tested with xUnit.
  \item \textit{Live: \href{http://167.99.59.173}{http://167.99.49.173} |
                Source: \href{https://github.com/maikeulb/rolleishop}{github.com/maikeulb/rolleishop}}
\end{itemize}

%\datedsubsection{\textbf{StationaryShop} | \textit{Python, Flask, PostgreSQL, Redis, JavaScript, Bootstrap 4, Docker, Nginx}}{}
%E-commerce application for stationary items.
%\begin{itemize}
%  \item Implemented catalog, shopping cart (cached with Redis), order processing (Stripe integration), full-text search, email confirmation, localization (translated to Japanese), and admin features. Deployed onto DigitalOcean VM and tested with Pytest.
%  \item \textit{Live: \href{http://167.99.53.140}{http://167.99.53.140} | 
%                Source: \href{https://github.com/maikeulb/stationaryshop}{github.com/maikeulb/stationaryshop}}
%\end{itemize}

\datedsubsection{\textbf{FriendMeetFriend} | \textit{Go, PostgreSQL, Docker}}{}
RESTful API backend for friend meeting application with token-based authentication system (using JWTs).
\begin{itemize}
   \item \textit{Source: \href{https://github.com/maikeulb/friend-meet-friend}{github.com/maikeulb/friend-meet-friend}}
\end{itemize}

%\datedsubsection{\textbf{FriendMeetFriend} | \textit{Go, PostgreSQL, Docker}}{}
%RESTful API backend for friend meeting application with token-based authentication system (using JWTs).
%\begin{itemize}
   %\item \textit{Source: \href{https://github.com/maikeulb/friend-meet-friend}{https://github.com/maikeulb/friend-meet-friend}}
%\end{itemize}

\datedsubsection{\textbf{ShotOnZeiss} | \textit{JavaScript, React/Redux, Ant Design, Firebase}}{}
Social network for Zeiss lovers: users share their favorite photos taken with
Zeiss lenses.
\begin{itemize}
   \item \textit{Live: \href{https://shotonzeiss.firebaseapp.com}{shotonzeiss.firebaseapp.com} |
                 Source: \href{https://github.com/maikeulb/shotonzeiss}{github.com/maikeulb/shotonzeiss}}
\end{itemize}


\section{\faUsers\ Employment}

\datedsubsection{\textbf{Gilsanz Murray Steficek} | New York City, New York}{Fall 2013 -- Summer 2017}
\role{Senior Structural Engineer }{ Manager: Ramon Gilsanz and Gary Steficek}
Design and analysis of new and existing structures.
\begin{itemize}
  \item Helped lead the design, analysis, and construction administration of the Woolworth Building
          condo renovations. 
  \item Assist the seismic risk analysis of the National Institute of Health Clinical Research Center.
\end{itemize}

\datedsubsection{\textbf{University of California, Berkeley} | Berkeley,
        California}{Fall 2010 -- Spring 2013}
\role{Graduate Student Researcher } {Advisor: Anil K. Chopra}
Finite Element Analysis of dam structures using LS-DYNA and EACD; Selecting and scaling earthquake ground motions.
\begin{itemize}
  \item Assist the development of dam analysis methodologies for the United States Bureau of
          Reclamation (USBR).
  \item Research spectrum-matching ground motions with wavelets.
\end{itemize}

\section{\faCogs\ Skills}

  \textbf{Programming Languages}: C\#, Java, Python, JavaScript/TypeScript, Go, Bash, and SQL

  %\textbf{Frameworks/Libraries}: ASP.NET Core, EF Core, Dapper, Flask, Node.js, React/Redux, and jQuery
  
  \textbf{Frameworks/Libraries}: ASP.NET Core, EF Core, Flask, SqlAlchemy, Node.js, React/Redux, Bootstrap 4, and jQuery

  %\textbf{Frameworks/Libraries}: ASP.NET Core, Flask, SqlAlchemy, Node.js, React/Redux, and jQuery

  \textbf{Technologies}: PostgreSQL, MySQL, MongoDB, Redis, Firebase, ElasticSearch, Celery, RabbitMQ, and Webpack
  
  %\textbf{Infrastructure}: DigitalOcean virtual machines and object storage, Gunicorn/Nginx, Docker, and PyTest
 
 % \textbf{Infrastructure}: DigitalOcean virtual machines and object storage, Kestrel/Nginx, Docker, and xUnit
  
  \textbf{Infrastructure}: DigitalOcean virtual machines and object storage, Nginx, Lets Encrypt, Docker, xUnit, and Pytest


\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of California, Berkeley}, Berkeley, CA}{Fall 2009 -- Spring 2010}
\textit{M.S } in Civil Engineering (Structures and Mechanics Emphasis), GPA: 3.6
\begin{itemize}
 \item National Science Foundation Graduate Researcher Fellowship (NSF GRFP)
 \item University of California, Berkeley Chancellor's Graduate Fellowship
\end{itemize}

\datedsubsection{\textbf{University of California, San Diego}, La Jolla, CA}{Fall 2005 -- Spring 2009}
\textit{B.S.} in Structural Engineering, Major GPA: 3.7
\begin{itemize}
    \item Tau Beta Pi (Engineering Honor Society)
\end{itemize}

\end{document}
